\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\footskip}{4pt} 
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.9cm, right=1.4cm, bottom=0.9cm}
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={},
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=3pt,
    arc=0pt,outer arc=0pt,
}

\urlstyle{same}
\raggedright

\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item #1}
\newcommand{\resumeSubheading}[4]{\vspace{0.5mm}\item
\begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & \textit{\footnotesize{#4}} \\
\textit{\footnotesize{#3}} &  \footnotesize{#2}\\
\end{tabular*}
\vspace{-2.5mm}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm,itemsep=0.5mm]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex,rightmargin=2ex,itemsep=0.2mm]\small}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{0.5mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-0.8mm}}
\newcommand{\cvsection}[1]{\vspace{1mm}
\begin{tcolorbox}
\textbf{\large #1}
\end{tcolorbox}
\vspace{-3mm}}

\linespread{1.05}
\newcommand{\name}{Alexander Peczon}
\newcommand{\phone}{510-435-6806}
\newcommand{\emaila}{peczonalex@gmail.com}

\begin{document}
\vspace{-8mm}
\begin{center}
\parbox{\dimexpr\linewidth-2.9cm\relax}{
\centering
\textbf{\Huge \name} \\
\vspace{1mm}
\footnotesize
\begin{tabularx}{\textwidth}{c} 
\faPhone\ +1-\phone \hspace{6mm} 
\faEnvelope\ \href{mailto:\emaila}{\emaila} \hspace{6mm} 
\faGithub\ \href{https://github.com/BakedSoups}{github.com/BakedSoups} \hspace{6mm} 
\faLinkedin\ \href{https://linkedin.com/in/apeczon}{linkedin.com/in/apeczon}
\end{tabularx}
}
\end{center}
\vspace{-5mm}

\section{\textbf{Education}}
\vspace{-3mm}
\resumeSubheading
{University of San Francisco} {}
{B.S. Computer Science}{Graduating 2026}
\begin{itemize}[leftmargin=0.1in,label={}]
\small{\item{Coursework: Linear Algebra, Statistics, Vector Calculus, Software Engineering, Computer Architecture}}
\end{itemize}
\vspace{-6mm}

\section{\textbf{Experience}}
\resumeSubHeadingListStart

\resumeSubheading
{Alaris Security}{San Francisco}
{Fullstack Engineer}{Aug 2025 – Present}
\vspace{-3mm}

\resumeItemListStart
  \resumeItem{Designed scalable data pipeline with Prefect + Airflow, processing 500K+ security events daily and improving analytics reliability by 60\%.}
  \resumeItem{Resolved critical UI bugs in React-based security platform, reducing system downtime by 90\% and improving user experience for 1000+ enterprise clients.}
  \resumeItem{Authored comprehensive platform-wide data flow documentation, enabling leadership to evaluate scaling solutions and reducing onboarding time for new engineers by 50\%.}
\resumeItemListEnd
\vspace{-3mm}

\resumeSubheading
{Future Tilt (Ecommerce Marketing Agency)}{San Francisco}
{Software Developer (Promoted from Intern)}{Jul 2025 – Present}
\vspace{-3mm}

\resumeItemListStart
  \resumeItem{Built an AI template builder that auto-generates email boilerplates, cutting design prep time by 40\%.}
  \resumeItem{Developed BigQuery dashboards analyzing 10M+ daily records, improving brand forecasting.}
  \resumeItem{Maintained an AWS Lambda + BigQuery alerting pipeline, reducing manual checks by 80\%.}
  \resumeItem{Automated Trello board updates via Lambda, streamlining campaign tracking for 15+ clients.}
  \resumeItem{Deployed ECS Dockerized Lambda for real-time revenue alerts, cutting lag from 24h to <1h.}
\resumeItemListEnd
\vspace{-3mm}

\resumeSubheading
{USF MAGIC Lab}{San Francisco}
{NLP Researcher}{Mar 2025 – Present}
\vspace{-3mm}

\resumeItemListStart
  \resumeItem{Built an ETL pipeline (BeautifulSoup) scraping 20k+ news articles for sentiment analysis.}
  \resumeItem{Developed SpaCy + NetworkX models to map sentiment and reveal bias trends.}
\resumeItemListEnd
\vspace{-3mm}

\resumeSubheading
{USF Strategic Enrollment Management}{San Francisco}
{Web Intern and Analyst}{Jul 2024 – Present}
\vspace{-3mm}

\resumeItemListStart
  \resumeItem{Created predictive models that improved enrollment forecasting accuracy by 15\%.}
  \resumeItem{Developed semantic search + Pandas system, reducing record reconciliation time by 50\%.}
  \resumeItem{Automated website updates with Python + Jinja2, cutting update time from hours to minutes.}
\resumeItemListEnd
\vspace{-3mm}


\resumeSubheading
{Students Assessing Teaching and Learning (SATAL)}{UC Merced}
{Data Analyst}{Dec 2023 – May 2024}
\vspace{-3mm}
\resumeItemListStart
  \resumeItem{Designed and conducted statistical analysis on 50+ classroom feedback surveys for educational improvement.}
  \resumeItem{Built ML classification system using LLMs + TensorFlow, achieving 99\% accuracy in response categorization.}
  \resumeItem{Processed complex XML-based Qualtrics survey data and created automated reporting systems for faculty.}
  \resumeItem{Applied NLP techniques to extract insights from open-ended survey responses.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-4mm}

\section{\textbf{Projects}}
\resumeSubHeadingListStart

\resumeSubheading
{NextSteamGame.com Recommendation Engine}{San Francisco}
{Vector Similarity Search \& Hierarchical Tagging}{Current}
\vspace{-3mm}

\resumeItemListStart
  \resumeItem{Scaled to 20k+ users and 1k daily visitors with a recommendation system for 22k+ Steam games.}
  \resumeItem{Built multi-source ETL (Steam API, YouTube, scraping) to process millions of reviews.}
  \resumeItem{Designed hierarchical genre tree + vector embeddings, improving relevance by 40\%.}
  \resumeItem{Generated procedural tags (art style, soundtrack, subjective features) for nuanced results.}
  \resumeItem{Optimized search with hierarchical fallback and vector pruning, achieving sub-second latency.}
\resumeItemListEnd
\vspace{-3mm}

\resumeSubheading
{Maldemic Pandemic Simulator}{San Francisco}
{Stochastic Modeling \& Deep Learning}{Dec 2024 – Feb 2025}
\vspace{-3mm}

\resumeItemListStart
  \resumeItem{Built a real-time epidemic simulator with a Markov chain + NN model trained on COVID-19 data.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-5mm}

\section{\textbf{Technical Skills}}
\begin{itemize}[leftmargin=0.1in,label={},itemsep=0mm,parsep=0mm,topsep=0mm]
\small{\item{
ML: PyTorch, TensorFlow, Keras, Scikit-learn, Hugging Face, OpenAI API \\
Programming: Python, SQL, JavaScript, React, C++, Go, NumPy, Pandas, Matplotlib, Seaborn, Docker, Kubernetes, Nginx, GraphQL, Plotly, Tableau \\
Databases: PostgreSQL, BigQuery, SQLite, ChromaDB, MongoDB, BigGraph, Airflow, Prefect, Qdraunt
}}
\end{itemize}

\end{document}